Synthesizing Symmetric Lenses

### 2018-07-12 papers/SymmetricLenses/main.tex
minor fixes

We describe an implementation of simple symmetric lenses and our synthesis
procedure as extensions to the Boomerang language~\cite{Boomerang}. We
evaluate
its performance on 48 benchmark examples drawn from FlashFill~\bcp{cite}, Augeus~\bcp{cite},
and an online collection of electronic file formats. Our
implementation can synthesize all these lenses in under
30 seconds. 
\end{abstract}

@@

We implemented the \GreedySynth and \Expand algorithms and evaluated their
effectiveness at synthesizing lenses on a benchmark suite of 48 problems,
including data cleaning tasks taken from Flash Fill~\cite{gulwani-popl-2014},
view maintenance tasks taken from Augeas~\cite{Augeas}, and ad hoc format
synchronization tasks taken from a variety of other locations\footnote{The
  majority of these format synchronization tasks were derived from the
  bidirectional programming literature.}.

@@

The algorithm for converting a stochastic regular expressions into its
corresponding stochastic DNF regular expressions, written
$\ToDNFRegexOf{\Regex}$, is defined below.\bcp{Could put this in two columns
to save space.}
\[
  \begin{array}{rcl}
    \ToDNFRegexOf{\String} & = & \DNFOf{(\SequenceOf{\String},1)}\\
    \ToDNFRegexOf{\emptyset} & = & \DNFOf{}\\
    \ToDNFRegexOf{(\PRegexStar{\Regex}{\Probability})} & = & \AtomToDNFOf{\PRegexStar{(\ToDNFRegexOf{\Regex})}{\Probability}}\\
    \ToDNFRegexOf{(\RegexConcat{\Regex_1}{\Regex_2})} & = & \ToDNFRegexOf{\Regex_1} \ConcatDNF \ToDNFRegexOf{\Regex_2}\\
    \ToDNFRegexOf{(\PRegexOr{\Regex_1}{\Regex_2}{\Probability})} & = & \ToDNFRegexOf{\Regex_1} \OrDNF_{\Probability} \ToDNFRegexOf{\Regex_2}\\
  \end{array}
\]
This conversion relies on operators defined in
Figure~\ref{fig:dnf-regex-functions}. We have proved that this conversion
respects languages and probability distributions.

@@

\begin{theorem}
  Let $\Lens$ be an asymmetric lens. $\Lens$ is also a simple symmetric lens,
  where:\bcp{This could be set in two columns.}
  \begin{center}
    \begin{tabular}{rcl}
      $\Lens.\CreateROf{x}$ & $=$ & $\Lens.get \App x$\\
      $\Lens.\CreateLOf{y}$ & $=$ & $\Lens.create \App y$\\
      $\Lens.\PutROf{x}{y}$ & $=$ & $\Lens.get \App x$\\
      $\Lens.\PutLOf{y}{x}$ & $=$ & $\Lens.put \App y \App x$
    \end{tabular}
  \end{center}
\end{theorem}

>>>>

We describe an implementation of simple symmetric lenses and our synthesis
procedure as extensions to the Boomerang language~\cite{Boomerang}. We evaluate
its performance on 48 benchmark examples drawn from Flash Fill~\cite{flashfill},
Augeus~\cite{augeas2}, the bidirectional programming literature, and electronic
file format synchronization tasks. Our implementation can synthesize all these
lenses in under 30 seconds.
\end{abstract}

@@

We implemented the \GreedySynth and \Expand algorithms and evaluated their
effectiveness at synthesizing lenses on a benchmark suite of 48 problems,
including data cleaning tasks taken from Flash Fill~\cite{gulwani-popl-2014},
view maintenance tasks taken from Augeas~\cite{Augeas}, and ad hoc format
synchronization tasks taken from a variety of other locations\footnote{The
  majority of these format synchronization tasks were taken from the
  bidirectional programming literature.}.

@@

The algorithm for converting a stochastic regular expressions into its
corresponding stochastic DNF regular expressions, written
$\ToDNFRegexOf{\Regex}$, is defined below.
\[
  \begin{array}{rcl@{\hspace*{3em}}rcl}
    \ToDNFRegexOf{\String} 
    & = 
    & \DNFOf{(\SequenceOf{\String},1)}

    & \ToDNFRegexOf{(\RegexConcat{\Regex_1}{\Regex_2})} 
    & = 
    & \ToDNFRegexOf{\Regex_1} \ConcatDNF \ToDNFRegexOf{\Regex_2} \\

    \ToDNFRegexOf{\emptyset} 
    & = 
    & \DNFOf{}

    & \ToDNFRegexOf{(\PRegexOr{\Regex_1}{\Regex_2}{\Probability})} 
    & = 
    & \ToDNFRegexOf{\Regex_1} \OrDNF_{\Probability} \ToDNFRegexOf{\Regex_2} \\

    \ToDNFRegexOf{(\PRegexStar{\Regex}{\Probability})} & = & \AtomToDNFOf{\PRegexStar{(\ToDNFRegexOf{\Regex})}{\Probability}}\\

  \end{array}
\]
This conversion relies on operators defined in
Figure~\ref{fig:dnf-regex-functions}. We have proved that this conversion
respects languages and probability distributions.

@@

\begin{theorem}
  Let $\Lens$ be an asymmetric lens. $\Lens$ is also a simple symmetric lens,
  where:
  \begin{center}
    \begin{tabular}{rcl@{\hspace*{3em}}rcl}
      $\Lens.\CreateLOf{y}$ & $=$ & $\Lens.create \App y$
      & $\Lens.\CreateROf{x}$ & $=$ & $\Lens.get \App x$\\
      $\Lens.\PutLOf{y}{x}$ & $=$ & $\Lens.put \App y \App x$
      & $\Lens.\PutROf{x}{y}$ & $=$ & $\Lens.get \App x$
    \end{tabular}
  \end{center}
\end{theorem}
